---
title: "Machine Learning Course Project"
author: "Eduardo Zamudio"
date: "6/15/2022"
output: html_document
---

```{r libraries and data source, include=FALSE,echo=TRUE}
library(caret)
library(randomForest)
#Load Information
link <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
training_Data_Set <- read.csv(url(link))
link <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
testing_Data_Set <- read.csv(url(link))
```

# Machine Learning Project

The goal of the project is to predict the manner in which they did the exercise,  the "classe" variable in the training set. The file use the database, of Velloso et.al (2013)

```{r filter information, include=FALSE}

##Analysis of information and deletion fo the NA variables

##Analysis of information

d<- apply(training_Data_Set , 2, function(x) {length(which(is.na(x)|x==""))/nrow(training_Data_Set)})
d <- data.frame(d)
d <- 1-d
training_Data_Set <- training_Data_Set[,which(d>0.9)]
testing_Data_Set <- testing_Data_Set[,which(d>0.9)]

```

## Cleaning the dataset

The dataset content some time tags and index column that has been deleted from the dataset, and one variable with nearzero variance

```{r pressure, include=FALSE}

##Delete the index column, names and time
training_Data_Set <- training_Data_Set[,-c(1:5)]
str(training_Data_Set)
##Delete near Zero Var predictors
training_Data_Set <- training_Data_Set[,-nearZeroVar(training_Data_Set)]
#Transform Class in factor 
training_Data_Set$classe <- as.factor(training_Data_Set$classe)
```


## Testing and training datasets

In accordance with the data volume, the data was splitted 60/40
```{r split, include=FALSE}
set.seed(1989898)
e<- createDataPartition(training_Data_Set$classe, p=0.6, list = FALSE)
training <- training_Data_Set[e,]
test <- training_Data_Set[-e,]
```

## Random Forest 

These algorithm suits remarkably to the dataset and has a high accuracy up to 99.9% in the training and test set

```{r training, cache=TRUE, echo=FALSE}
clasiffier <- randomForest(x = training_Data_Set[,-54], y = training_Data_Set[,ncol(training_Data_Set)],ntree = 500)
y_pred <- predict(clasiffier, newdata = test[,-54])
table(y_pred,test[,54])
```

##Quizz 

```{R Quizz, include = FALSE,}
nearZeroVar(training_Data_Set)
```
##Reference
Velloso, E.; Bulling, A.; Gellersen, H.; Ugulino, W.; Fuks, H. Qualitative Activity Recognition of Weight Lifting Exercises. Proceedings of 4th International Conference in Cooperation with SIGCHI (Augmented Human '13) . Stuttgart, Germany: ACM SIGCHI, 2013.
